Optimal (Multiway) Spatial Joins

### 2024-06-01 msj.tex
yufei

It is worth noting that $\Omega(n \log n)$ is a lower bound on the runtime of any comparison-based algorithm  solving the $k$-SJ problem (see Appendix~\ref{app:comp-class} for a formal definition of such algorithms), even for $k = 2$. This can be established via a reduction from the {\em element distinctness} (ED) problem; see \cite{dl79}.

@@

An algorithm is {\em correct} if it produces the correct output on all $(n_1, n_2, ..., n_k)$-inputs. Its {\em worst-case cost} is the height of $\T$.

>>>>

It is worth noting that $\Omega(n \log n)$ is a lower bound on the runtime of any comparison-based algorithm  solving the $k$-SJ problem (see Appendix~\ref{app:comp-class} for a formal definition of such algorithms), even for $k = 2$. This can be established via a reduction from the {\em element distinctness} problem; see \cite{dl79}.

@@

The algorithm is {\em correct} if it produces the correct output on all $(n_1, n_2, ..., n_k)$-inputs. Its {\em worst-case cost} is the height of $\T$.

As mentioned in Section~\ref{sec:intro:prev}, through a reduction from the element distinctness problem \cite{dl79}, one can show that when $k = 2$, any comparison-based algorithm capable of solving all $(n/2, n/2)$-inputs must have a worst-case cost of $\Omega(n \log n)$.
